Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-01-13 1.intro/introduction.tex
edit up to Chapter 2; leaving some for discussion.

The proliferation of information technology has enabled us to collect and consume huge volumes of data at unprecedented speeds and at very low costs.
This fast and cheap access to data gave rise to fundamentally new ways of pursuing scientific questions.
In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, \stilian{nowadays abundant data}{abundant information} are often available before specific questions are even formulated. 
Such \stilian{data}{information} can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
As a result, {multiple testing} --- where a large number of hypotheses are formulated and screened for their plausibility simultaneously --- has become a staple of modern data-driven studies.

An archetypal example of multiple testing problems is genetic association studies \citep{bush2012genome}.
In genetic association studies, scientists test hypotheses relating each of the hundreds of thousands of genetic marker locations to phenotypic traits of interest;
the goal here is to select the set of most promising genetic markers for subsequent investigation.
Another example of multiple testing problems arise in cybersecurity, where millions of IP addresses are monitored in real time.
In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities. Thus, malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.

We are motivated by the above examples in particular to study {high-dimensional} multiple testing problems where a large number of hypotheses are tested simultaneously.

% This high multiplicity of tests brings along a multitude of challenges, and has been a subject of extensive study in recent years.

In the rest of the introduction, we shall review the main objectives of high-dimensional multiple testing, elaborate on these objectives in two classes of data models and in the context of the genetic applications, and briefly summarize the contents of this text.

% While many such multiplicities are explicit, where screenings and selections of hypotheses, models, or variables are performed \emph{and} annouced, they may be completely ``silent'', where such selections are performed but not explicitly reported \citep{berry2012multiplicities}.

% This paper seeks to establish some new asymptotic optimality results for common multiple testing procedures, including the Bonferroni procedure and the Benjamini-Hochberg procedure, in high-dimensional chi-square models.

% This dissertation studies in detail the theoretical limits of multiple problems in high-dimensional sparse models

@@

\begin{enumerate}
\item [{\rm I.}] (signal detection or {\em testing}) To detect the presence of non-zero components in $\mu$. That is, to test the global hypothesis $\mu = 0$, which we call the \emph{detection} problem, and\\

\item[{\rm II.}] (support estimation or {\em inference})
 To estimate the support set $S$, which we call the \emph{support recovery} problem.
\end{enumerate}
\medskip
To illustrate, in the engineering application of cybersecurity, Internet service providers (ISP) routinely monitor a large number of network traffic streams to determine 
if there are abnormal surges, blackouts, or other types of anomalies.  The data vector $x$ could represent, for example, incoming traffic volumes to each server 
node, internet protocol (IP) address, or port that the ISP monitors.  In this case, the vector $\mu$ represents the average traffic volumes in each of the streams 
under normal operating conditions, and $\epsilon$'s -- the fluctuations around these normal levels of traffic.  
% The ISPs collect, for example, incoming traffic volumes to each server to determine if there are abnormal surges or blackouts.
The signal detection problem in this context is then equivalent to determining if there are \emph{any} anomalies among all data streams, and the support recovery problem is equivalent to \emph{identifying} the streams experiencing anomalies.  
%The dimension of $x$ (number of streams) is typically very large, while the non-trivial 
%signal is sparse (relatively few data streams experience anomalies).
Similar questions of signal detection and support recovery are pursued in large-scale microarray experiments \citep{dudoit2003multiple},
brain imaging and fMRI analysis \citep{nichols2003controlling}, and numerous other anomaly detection applications.

@@

Model \eqref{eq:model-additive} is simple yet ubiquitous.
Consider the linear model
\begin{equation*}
 Y = X\mu + \xi,
\end{equation*}
where $\mu$ is a $p$-dimensional vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
If the design matrix $X$ is of full column rank, then the ordinary least squares (OLS) estimator of $\mu$ can be formed 
\begin{equation} \label{eq:OLS}
    \widehat{\mu} = \left(X'X\right)^{-1}X'Y = \mu + \epsilon,
\end{equation}
where $\epsilon := (X'X)^{-1}X'\xi$. \stilian{R2, Typo 2 -- \fbox{DISCUSS} }{I see no problems here except that we are not in the high-dimensional regime $p\gg n$. If we were to address that, we need to expand the discussion. 1) Talk about sparsity of $\mu$ 2) Introduce the assumption that if ${\rm supp}(\mu) = r <n$, then every $r$ of the $p$ columns of 
$X$ must be linearly independent -- is there a name for such a condition in the literature? We know it happens with probability one if $X$ has independent, say Gaussian, entries.  3) Then, it seems clear that the support of $\mu$ will be identifiable if we replace the inverse with a Moore-Penrose inverse. BTW, an intriguing question: Given a design matrix $X$, consider the quantity:
$$
c_r(X) :=\min_{w\subset \{1,\cdots,p\},\ |w| = r} {\| (X_w' X_w)^{-1}\| \over \| X_w'X_w\| },
$$
where the minimum is taken over all subsets of indices $w$ with cardinality $r<n$ and $X_w:= (x_{i,j})_{j\in w}$ is the sub-matrix of $X$ obtained
by selecting the columns indexed by the elements in $w\subset\{1,\cdots,p\}$.  Intuitively, $c_r(X)$ gives us the overall difficulty of identifying a 
sparse signal $\mu$ with support of size $r$. \fbox{Going off on a tangent here...}}
Hence we recover the generic problem \eqref{eq:model-additive}. 
Signal detection is therefore equivalent to the problem of testing the global null model, and support recovery problem corresponds to the fundamental problem of variable selection.

Note that the components of the observation vector $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, 
unless we have an orthogonal design. Indeed, in practice, independence is the exception rather than the rule.
Therefore, a general theory of feasibility must address the role of the {\em error dependence} structure in such testing and support estimation 
problems.  It is also important to identify practical and/or optimal procedures that attain the performance limits in independent as well as dependent cases, as soon 
as the problems become theoretically feasible.  We address both themes in this text.

>>>>

The proliferation of information technology has enabled us to collect and consume huge volumes of data at unprecedented speeds and at very low costs.
This convenient access to data gave rise to a fundamentally different way of pursuing scientific questions.
In contrast with the traditional hypothesis--experiment--analysis cycle where data are collected from the experiments, nowadays abundant data are often available before specific questions are even formulated. 
Such data can be used for not just evaluating hypotheses, but also for \emph{generating}, and \emph{selecting} the hypotheses to pursue. 
As a result, {multiple testing} --- where a large number of hypotheses are formulated and screened for their plausibility simultaneously --- has become a staple of modern data-driven studies.

An archetypal example of multiple testing problems is genetic association studies \citep{bush2012genome}.
In these studies, scientists test hypotheses relating each of the hundreds of thousands of genetic marker locations to phenotypic traits of interest.
For a phenotypic trait on which we have little prior knowledge, we cannot simply test for association on one or a few specific genetic locations, as there are often not enough empirical evidence or biological theory to pin point these genetic locations in the first place.
Rather, the goal here is to select the set of most promising genetic markers from a large number of candidate locations for subsequent investigation.

Another example of multiple testing problems arise in cybersecurity, where millions of IP addresses are monitored in real time.
In this engineering application, statistics are collected and tests are performed for each IP address, in an attempt to locate the IP addresses with anomalous network activities, so that and malicious traffic and volumetric attacks can be filtered to protect end users of network services \citep{kallitsis2016amon}.
Similar to the genetic application above, we use data to search over candidate IP addresses and identify locations of interest.

We are motivated very much by these examples to study {high-dimensional} multiple testing problems where a large number of hypotheses are tested simultaneously.
% This high multiplicity of tests brings along a multitude of challenges, and has been a subject of extensive study in recent years.
In the rest of the introduction, we shall more review the main objectives of high-dimensional multiple testing, and elaborate on these objectives with two classes of data models in the context of various applications.

@@

\begin{enumerate}
\item [{\rm I.}] \emph{Signal detection}: to detect the presence of non-zero components in $\mu$. That is, to test the global hypothesis $\mu = 0$. \\

\item[{\rm II.}] \emph{Support recovery}: to estimate the support set $S$. This is also sometimes referred to as the \emph{support estimation} or \emph{signal identification} problem.
\end{enumerate}
\medskip
To illustrate, in the engineering application of cybersecurity, Internet service providers (ISP) routinely monitor a large number of network traffic streams to determine 
if there are abnormal surges, blackouts, or other types of anomalies.  The data vector $x$ could represent, for example, incoming traffic volumes to each server 
node, internet protocol (IP) address, or port that the ISP monitors.  In this case, the vector $\mu$ represents the average traffic volumes in each of the streams 
under normal operating conditions, and $\epsilon$'s -- the fluctuations around these normal levels of traffic.  
% The ISPs collect, for example, incoming traffic volumes to each server to determine if there are abnormal surges or blackouts.
The signal detection problem in this context is then equivalent to determining if there are \emph{any} anomalies among all data streams, and the support recovery problem is equivalent to \emph{identifying} the streams experiencing anomalies.  
%The dimension of $x$ (number of streams) is typically very large, while the non-trivial 
%signal is sparse (relatively few data streams experience anomalies).
Similar questions of signal detection and support recovery are pursued in large-scale microarray experiments \citep{dudoit2003multiple},
brain imaging and fMRI analysis \citep{nichols2003controlling}, and numerous other anomaly detection applications.

@@

Model \eqref{eq:model-additive} is simple yet ubiquitous.
Consider the linear model
\begin{equation*}
 Y = X\mu + \xi,
\end{equation*}
where $\mu$ is a $p$-dimensional vector of regression coefficients of interest to be inferred from observations of $X$ and $Y$.
If the design matrix $X$ is of full column rank\footnote{This, of course, requires that we have more samples than dimensions, i.e., $n>p$. Nevertheless, multiplicity of tests is still present when $p$ itself is large -- the multiple testing problem is by no means exclusive to situations where $p\gg n$.}, then the ordinary least squares (OLS) estimator of $\mu$ can be formed 
\begin{equation} \label{eq:OLS}
    \widehat{\mu} = \left(X'X\right)^{-1}X'Y = \mu + \epsilon,
\end{equation}
where $\epsilon := (X'X)^{-1}X'\xi$. 
% \stilian{R2, Typo 2 -- \fbox{DISCUSS} }{I see no problems here except that we are not in the high-dimensional regime $p\gg n$. If we were to address that, we need to expand the discussion. 1) Talk about sparsity of $\mu$ 2) Introduce the assumption that if ${\rm supp}(\mu) = r <n$, then every $r$ of the $p$ columns of $X$ must be linearly independent -- is there a name for such a condition in the literature? We know it happens with probability one if $X$ has independent, say Gaussian, entries.  3) Then, it seems clear that the support of $\mu$ will be identifiable if we replace the inverse with a Moore-Penrose inverse. BTW, an intriguing question: Given a design matrix $X$, consider the quantity:
% $$
% c_r(X) :=\min_{w\subset \{1,\cdots,p\},\ |w| = r} {\| (X_w' X_w)^{-1}\| \over \| X_w'X_w\| },
% $$
% where the minimum is taken over all subsets of indices $w$ with cardinality $r<n$ and $X_w:= (x_{i,j})_{j\in w}$ is the sub-matrix of $X$ obtained by selecting the columns indexed by the elements in $w\subset\{1,\cdots,p\}$.  Intuitively, $c_r(X)$ gives us the overall difficulty of identifying a sparse signal $\mu$ with support of size $r$. \fbox{Going off on a tangent here...}}
Hence we recover the generic problem \eqref{eq:model-additive}. 
Signal detection is therefore equivalent to the problem of testing the global null model, and support recovery problem corresponds to the fundamental problem of variable selection.

Note that the components of the observation vector $x$ (and equivalently, the noise $\epsilon$) in \eqref{eq:model-additive} need not be independent. 
In the linear regression example, even when the components of the noise term $\xi$ are independent, those of the OLS estimator \eqref{eq:OLS} need not be, except in the case of orthogonal designs.
Indeed, in practice, independence is the exception rather than the rule.
Therefore, a general theory of feasibility must address the role of the {\em error dependence} structure in such testing and support estimation 
problems.
It is also important to identify practical and/or optimal procedures that attain the performance limits in independent as well as dependent cases, as soon as the problems become theoretically feasible.  We address both themes in this text.

### 2021-01-13 2.background/2.statistical_procedures.tex
edit up to Chapter 2; leaving some for discussion.

{\bf Signal detection.}
One of the commonly used statistics in sparse signal detection problems such as \eqref{eq:global-test-additive} and \eqref{eq:global-test-chisq} are the $L_q$ norms of the observations $x$,
\begin{equation} \label{eq:Lq-norm}
   L_q(x) = \left(\sum_{i=1}^p{|x(i)|^q}\right)^{1/q}.
\end{equation}
Typical choices of $q$ include $q=1, 2$ and $\infty$, where $L_\infty(x)$ is interpreted as the limit of $L_q(x)$ norms as $q\to\infty$, and is equivalent to $\max_{i}|x(i)|$.
Test procedures based on \eqref{eq:Lq-norm} may then be written as $\mathcal{R}(x) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.

While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., 
we have a one-sided alternative
\begin{equation} \label{eq:global-test-one-sided}
    %\mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    %\quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\}.
\end{equation}
Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
\stilian{Replacing $S$ with $T$}{\fbox{Pls check}}
\begin{equation} \label{eq:sum-statistic}
    T(x) := \sum_{i=1}^p{x(i)},
\end{equation}
or the maximum of the observations,
\begin{equation} \label{eq:max-statistic}
    M(x) := \max_{i=1,\ldots,p}{x(i)}.
\end{equation}
Other tests based on the empirical \ac{CDF} are also available.
Assuming the same one-sided alternative, let \stilian{Replacing $p(i)$ with $v(i)$ to avoid confusing with $p$}{\fbox{pls check}}
\begin{equation}
    v(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
\end{equation}
be the p-values of the individual observations, where $F_i$ is the \ac{CDF} of the $i$-th component $x(i)$ under $\mathcal{H}_0$.
We define empirical \ac{CDF} of the p-values as
\begin{equation}
    \widehat{F}_p(t) = 
    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(v(i)).
\end{equation}
Viewed as random elements in the space of c\`adl\`ag functions with the Skorohod $J_1$ topology, the centered and scaled \ac{CDF}s converge weakly to a Brownian bridge,
\begin{equation*}
    \left\{\sqrt{p}\left(\widehat{F}_p(t) - t\right)\right\}_{t\in[0,1]} 
    % \stackrel{J_1}{\longrightarrow} 
    \implies
    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},\ \ \ \mbox{ as } p\to\infty,
\end{equation*}
under the global null $\mathcal{H}_0$ and mild continuity assumptions on the $F_i$'s \citep{skorokhod1956limit}. 
Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
Of particular interest is the higher criticism (\ac{HC}) statistic, first proposed by \cite{tukey1976lecture},
\begin{equation} \label{eq:HC-statistic}
    HC(x) = 
    \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
\end{equation}

\stilian{Each of the above statistics $L_q, T, M,$ or $HC$, gives rise to a decision rule, whereby the null hypothesis is rejected if 
the statistic exceeds a suitably calibrated threshold. The choice of the threshold is typically determined based on large-sample limit 
theorems. For example, as shown in Theorem 1.1 of \cite{donoho2004higher}, under the null hypothesis
$$
 \frac{HC(x)}{\sqrt{2\log\log(p)}} \longrightarrow  1,\ \ \mbox{ in probability,}
$$ 
as $p\to\infty$.  Thus, one decision rule is to reject ${\cal H}_0$, if $HC(x)> t(p,\alpha_p)$, where 
$t(p,\alpha_p) = \sqrt{2\log\log(p)}(1+o(1))$.  As we will see, this yields an optimal signal detection procedure 
\citep[see also Theorem 1.2 in ][]{donoho2004higher}.}{\fbox{added} Agree?} The performance of these statistics in high-dimensional 
sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.

@@

Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \citep{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the \stilian{R2,Typo 3}{fixed} Cand\`es-Barber procedure \citep{barber2015controlling}.
Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
% \cite{roquain2011type}.

@@

We review five thresholding procedures, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
\begin{definition}[Bonferroni's procedure]
Suppose the errors $\epsilon(i)$'s have a common marginal distribution $F$, Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
\begin{equation} \label{eq:Bonferroni-procedure}
    t_p = F^{\leftarrow}(1 - \alpha/p).
\end{equation}
where  $F^{\leftarrow}(u)=\inf{\left\{x:F(x)\ge u\right\}}$ is the generalized inverse function.
\end{definition}
% It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
The Bonferroni procedure is deterministic (i.e., non data-dependent), and only depends on the dimension of the problem and the null distribution.
A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
which is a more aggressive (and also deterministic) thresholding procedure that uses the threshold
\begin{equation} \label{eq:Sidak-procedure}
    t_p = F^{\leftarrow}((1 - \alpha)^{1/p}).
\end{equation}
% can be shown to control FWER in the case independent errors.

The third procedure, strictly more powerful than Bonferroni's, is the so-called Holm's procedure \citep{holm1979simple}.
On observing the data $x$, its coordinates can be ordered from largest to smallest
$x(i_1) \ge x(i_2)  \ge \ldots \ge x(i_p)$,
where $(i_1, \ldots, i_p)$ is a permutation of $\{1, \ldots, p\}$. 
Denote the order statistics as $x_{[1]}, x_{[2]}, \ldots, x_{[p]}$.
\begin{definition}[Holm's procedure]
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1),\quad \text{for all }\;i\le i^*.
$$
Holm's procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:Holm-procedure}
    t_p(x) = x_{[i^*]}.
\end{equation}
\end{definition}
In contrast to the Bonferroni procedure, Holm's procedure is data-dependent.
% It can be shown that Holm's procedure also controls FWER at $\alpha$ level, regardless of dependence in the data.
A closely related, more aggressive (and also data-dependent) thresholding procedure is Hochberg's procedure \citep{hochberg1988sharper}.
%\begin{definition}[Hochberg's procedure]
%Hochberg's procedure 
It replaces the index $i^*$ in Holm's procedure with the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1).
$$
Notice that both Holm's and Hochberg's procedures compare p-values to the same thresholds $\alpha / (p-i+1)$.
However, Holm's procedure only rejects the set of hypotheses whose p-values are all smaller than their respective thresholds.
On the other hand, Hochberg's procedure rejects the set of hypotheses as long as the largest of their p-values fall below its threshold, and therefore, can be more powerful than Holm's procedure. 
%where  $\overline{F}(x)=1-F(x)$ is the survival function.
%\end{definition}

It can be shown that Bonferroni's and Holm's procedures both control FWER at their nominal levels, regardless of dependence in the 
data \citep{holm1979simple}. In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}. \stilian{DISCUSS}{Explain in the Supplement?}

@@

Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
\begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha i/p.
$$
The Benjamini-Hochberg (BH) procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:BH-procedure}
    t_p(x) = x_{[i^*]},
\end{equation}
\end{definition}
The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under \stilian{certain models of}{\fbox{added} correct?} dependent observations \citep{benjamini2001control}.

>>>>

{\bf Signal detection.}
One of the commonly used statistics in sparse signal detection problems such as \eqref{eq:global-test-additive} and \eqref{eq:global-test-chisq} are the $L_q$ norms of the observations $x$,
\begin{equation} \label{eq:Lq-norm}
   L_q(x) = \left(\sum_{i=1}^p{|x(i)|^q}\right)^{1/q}.
\end{equation}
Typical choices of $q$ include $q=1, 2$ and $\infty$, where $L_\infty(x)$ is interpreted as the limit of $L_q(x)$ norms as $q\to\infty$, and is equivalent to $\max_{i}|x(i)|$.
Test procedures based on \eqref{eq:Lq-norm} may then be written as $T(\mathcal{R}(x)) = \mathbbm{1}_{(t,+\infty)}(L_q(x))$, where the cutoff $t$ can be chosen to control the Type I error at desired levels.

While \eqref{eq:Lq-norm} measures the deviation of the data from the origin in an omnidirectional manner, statistics that are tailored to the alternatives can be used in the hopes of power improvement if the directions of the alternatives are known.
For example, in the additive error model \eqref{eq:model-additive}, suppose we want to test for positive mean shifts, i.e., one-sided alternative
\begin{equation} \label{eq:global-test-one-sided}
    %\mathcal{H}_0: \mu(i) = 0, \;i=1,\ldots,p,
    %\quad\text{v.s.}\quad 
    \mathcal{H}_1: \mu(i)> 0, \; \text{for some }i\in\{1,\ldots,p\}.
\end{equation}
Then, one might consider monitoring the sum (or equivalently, the arithmetic average) of the observations, 
\begin{equation} \label{eq:sum-statistic}
    S(x) := \sum_{i=1}^p{x(i)},
\end{equation}
or the maximum of the observations,
\begin{equation} \label{eq:max-statistic}
    M(x) := \max_{i=1,\ldots,p}{x(i)}.
\end{equation}
Other tests based on the empirical \ac{CDF} are also available.
Assuming the same one-sided alternative, let 
\begin{equation}
    q(i) = 1 - \sup\{F_i(y)\,:\,y<x(i)\}, \quad i = 1,\ldots,p,
\end{equation}
be the p-values of the individual observations, where $F_i$ is the \ac{CDF} of the $i$-th component $x(i)$ under $\mathcal{H}_0$.
We define empirical \ac{CDF} of the p-values as
\begin{equation}
    \widehat{F}_p(t) = 
    \frac{1}{p} \sum_{i=1}^p \mathbbm{1}_{[0, t]}(q(i)).
\end{equation}
Viewed as random elements in the space of c\`adl\`ag functions with the Skorohod $J_1$ topology, the centered and scaled \ac{CDF}s converge weakly to a Brownian bridge,
\begin{equation*}
    \left\{\sqrt{p}\left(\widehat{F}_p(t) - t\right)\right\}_{t\in[0,1]} 
    % \stackrel{J_1}{\longrightarrow} 
    \implies
    \left\{\mathbb{B}(t)\right\}_{t\in[0,1]},\ \ \ \mbox{ as } p\to\infty,
\end{equation*}
under the global null $\mathcal{H}_0$ and mild continuity assumptions on the $F_i$'s \citep{skorokhod1956limit}. 
Therefore, goodness-of-fit statistics such as Kolmogorov-Smirnov distance \citep{smirnov1948table}, Cramer-von Mises-type statistics \citep{cramer1928composition, anderson1952asymptotic} that measure the departure from this limiting behavior can be used for testing $\mathcal{H}_0$ against $\mathcal{H}_1$.
Of particular interest is the higher criticism (\ac{HC}) statistic, first proposed by \cite{tukey1976lecture},
\begin{equation} \label{eq:HC-statistic}
    HC(x) = 
    \max_{0\le t\le\alpha_0}\frac{\widehat{F}_p(t) - t}{\sqrt{t(1 - t)/p}}.
\end{equation}

Each of the above statistics $L_q$, $S$, $M$, or $HC$, gives rise to a decision rule, whereby the null hypothesis is rejected if 
the statistic exceeds a suitably calibrated threshold. The choice of the threshold is typically determined based on large-sample limit 
theorems. For example, as shown in Theorem 1.1 of \cite{donoho2004higher}, under the null hypothesis
$$
 \frac{HC(x)}{\sqrt{2\log\log(p)}} \longrightarrow  1,\ \ \mbox{ in probability,}
$$ 
as $p\to\infty$.  Thus, one decision rule is to reject ${\cal H}_0$, if $HC(x)> t(p,\alpha_p)$, where 
$t(p,\alpha_p) = \sqrt{2\log\log(p)}(1+o(1))$.  As we will see, this yields an optimal signal detection procedure 
\citep[see also Theorem 1.2 in ][]{donoho2004higher}. The performance of these statistics in high-dimensional 
sparse signal detection problems will be reviewed in Section \ref{sec:asymptotics}, and analyzed in Chapter \ref{chap:phase-transitions}.

@@

Examples of thresholding procedures include ones that aim to control FWER \eqref{eq:FWER-FWNR} --- Bonferroni's \citep{dunn1961multiple}, Sid\'ak's \citep{vsidak1967rectangular}, Holm's \citep{holm1979simple}, and Hochberg's procedure \citep{hochberg1988sharper} --- as well as procedures that target FDR \eqref{eq:FDR-FNR}, such as the Benjamini-Hochberg \cite{benjamini1995controlling} and the Barber-Cand\`es procedure \citep{barber2015controlling}.
Indeed, the class of thresholding procedures \eqref{eq:thresholding-procedure} is so general that it contains most (but not all) of the statistical procedures in the multiple testing literature.
% \cite{roquain2011type}.

@@

Under the assumption that the data $x(i)$'s under the null have a common marginal distribution $F$, we review five thresholding procedures for support recovery, starting with the well-known Bonferroni's procedure which aims at controlling family-wise error rates.
\begin{definition}[Bonferroni's procedure]
Bonferroni's procedure with level $\alpha$ is the thresholding procedure that uses the threshold
\begin{equation} \label{eq:Bonferroni-procedure}
    t_p = F^{\leftarrow}(1 - \alpha/p).
\end{equation}
where  $F^{\leftarrow}(u)=\inf{\left\{x:F(x)\ge u\right\}}$ is the generalized inverse function.
\end{definition}
% It is easy to see that the family-wise error rate (FWER) is controlled at level $\alpha$ by applying the union bound, regardless of the error-dependence structure (see e.g.\ Relation \eqref{eq:Bonferroni-FWER-control}, below).
The Bonferroni procedure is deterministic, i.e. non data-dependent, and only depends on the dimension of the problem and the null distribution.
A closely related procedure is Sid\'ak's procedure \citep{vsidak1967rectangular},
which is a more aggressive (and also deterministic) thresholding procedure that uses the threshold
\begin{equation} \label{eq:Sidak-procedure}
    t_p = F^{\leftarrow}((1 - \alpha)^{1/p}).
\end{equation}
% can be shown to control FWER in the case independent errors.

The third procedure, strictly more powerful than Bonferroni's, is the so-called Holm's procedure \citep{holm1979simple}.
On observing the data $x$, its coordinates can be ordered from largest to smallest
$x(i_1) \ge x(i_2)  \ge \ldots \ge x(i_p)$,
where $(i_1, \ldots, i_p)$ is a permutation of $\{1, \ldots, p\}$. 
Denote these order statistics as $x_{[1]}, x_{[2]}, \ldots, x_{[p]}$.
\begin{definition}[Holm's procedure]
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1),\quad \text{for all }\;i\le i^*.
$$
Holm's procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:Holm-procedure}
    t_p(x) = x_{[i^*]}.
\end{equation}
\end{definition}
In contrast to the Bonferroni procedure, Holm's procedure is data-dependent.
% It can be shown that Holm's procedure also controls FWER at $\alpha$ level, regardless of dependence in the data.
A closely related, more aggressive (and also data-dependent) thresholding procedure is Hochberg's procedure \citep{hochberg1988sharper}.
%\begin{definition}[Hochberg's procedure]
%Hochberg's procedure 
It replaces the index $i^*$ in Holm's procedure with the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha / (p-i+1).
$$
Notice that both Holm's and Hochberg's procedures compare p-values to the same thresholds $\alpha / (p-i+1)$.
However, Holm's procedure only rejects the set of hypotheses whose p-values are all smaller than their respective thresholds.
On the other hand, Hochberg's procedure rejects the set of hypotheses as long as the largest of their p-values fall below its threshold, and therefore, can be more powerful than Holm's procedure. 
%where  $\overline{F}(x)=1-F(x)$ is the survival function.
%\end{definition}

It can be shown that both Bonferroni's and Holm's procedures control FWER at their nominal levels, regardless of dependence in the 
data \citep{holm1979simple}. In contrast, Sid\'ak's and Hochberg's procedures control FWER at nominal levels when data are independent \citep{vsidak1967rectangular, hochberg1988sharper}. \stilian{DISCUSS}{Explain in the Supplement?}

@@

Recall the order statistics of our observations $x_{[1]} \ge x_{[2]}  \ge \ldots \ge x_{[p]}$.
\begin{definition}[Benjamini-Hochberg's procedure] \label{def:BH}
Let $i^*$ be the largest index such that
$$
\overline{F}(x_{[i]}) \le \alpha i/p.
$$
The Benjamini-Hochberg (BH) procedure with level $\alpha$ is the thresholding procedure with threshold
\begin{equation} \label{eq:BH-procedure}
    t_p(x) = x_{[i^*]},
\end{equation}
\end{definition}
The \ac{BH} procedure is shown to control the FDR at level $\alpha$ when the $x(i)$'s are independent \citep{benjamini1995controlling}. 
\stilian{DISCUSS}{Again, explain in the Supplement?} Variations of this procedure have been proposed to control the \ac{FDR} under certain models of dependent observations \citep{benjamini2001control}.
